\center Towards Globally Color-Dual All-Loop Integrands

### 2023-08-17 notes/2loopNLSM.tex
Added comment command for myself.
review sections and some appendices

\documentclass[11pt,letter]{article}
\usepackage{jheppub}
\usepackage{amsmath,amssymb}
\usepackage[dvipsnames]{xcolor}
%\usepackage{hyperref}
\usepackage{xspace}
\usepackage{ifdraft}
\usepackage{epstopdf}
\usepackage{slashed}
\usepackage{diagbox}
\usepackage{colortbl}
\usepackage{bbold}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{stackengine}
\def\RA{\rlap{\scalebox{1.6}{$\leftrightarrow$}}}
\def\DA{\smash{\bclap{\scalebox{1.6}{$\downarrow$}}}}
\def\mystrut{\rule[-2ex]{0ex}{6ex}}

@@

\tikzset{graviton/.style={decorate, decoration={snake, amplitude=.4mm, segment length=1.5mm, pre length=.5mm, post length=.5mm}, double}}
\tikzfeynmanset{compat=1.1.0}
%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
%\usetikzlibrary{external}  
%          %% Load the `external` library
%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
%\tikzexternalize[                     %% Activate externalization
%  prefix=images/,                    %% Avoid cluttering the directory
% system call={                       %% Use lualatex in system call
%    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
%  },
%]
\tikzfeynmanset{
  fermion2/.style={
    /tikz/postaction={
      /tikz/decoration={
        markings,
        mark=at position 0.7 with {
          \arrow{>[length=6pt, width=7pt]};
        },
      },
      /tikz/decorate=true,
    },
  },
}

@@

%%% Jacobi 1 %%%

\newcommand{\JacobiOneDoubleBox}{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1.5,1){4};
\vertex (a2) at (1.5,-1){2};
\vertex (a3) at (1.5,1){3};
\vertex (a4) at (-1.5,-1){1};
\vertex (mid1) at (0,-.5);
\vertex (mid2) at (0,.5);
\vertex (mid3) at (1,.5) ;
\vertex (mid4) at (1,-.5) ;
\vertex (mid5) at (-1,.5);
\vertex (mid6) at (-1,-.5) ;
\diagram{
(a4) --[ultra thick,](mid6),
(a3) --[ultra thick,](mid3),
(a2) --[ultra thick,](mid4),
(a1) --[ultra thick,](mid5),
(mid1) --[ultra thick,](mid2),
(mid3) --[ultra thick,](mid2),
(mid1) --[ultra thick,](mid6),
(mid1) --[ultra thick,](mid4),
(mid5) --[ultra thick,red](mid2),
(mid5) --[ultra thick,](mid6),
(mid3) --[ultra thick,](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

\newcommand{\JacobiOneCrossedBox}{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1.5,1){4};
\vertex (a2) at (1.5,-1){2};
\vertex (a3) at (1.5,1){3};
\vertex (a4) at (-1.5,-1){1};
\vertex (mid1) at (0,-.5);
\vertex (mid2) at (0,.5);
\vertex (mid3) at (1,.5);
\vertex (mid4) at (1,-.5);
\vertex (mid5) at (-1,.5);
\vertex (mid6) at (-1,-.5);
\vertex (mid7) at (-.5,0) {};
\diagram{
(a4) --[ultra thick,](mid6),
(a3) --[ultra thick,](mid3),
(a2) --[ultra thick,](mid4),
(a1) --[ultra thick,](mid5),
(mid1) --[ultra thick,](mid6),
(mid3) --[ultra thick,](mid2),
(mid1) --[ultra thick,](mid4),
(mid5) --[ultra thick,](mid7),
(mid7) --[ultra thick,](mid1),
(mid2) --[ultra thick,](mid6),
(mid5) --[ultra thick,red](mid2),
(mid3) --[ultra thick,](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

\newcommand{\JacobiOnePentaTriangle}{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1.5,1){4};
\vertex (a2) at (.5,-1){2};
\vertex (a3) at (.5,1){3};
\vertex (a4) at (-1.5,-1){1};
\vertex (mid1) at (-.5,-.5);
\vertex (mid2) at (-1,0);
\vertex (mid3) at (0,.5) ;
\vertex (mid4) at (0,-.5) ;
\vertex (mid5) at (-1,.5);
\vertex (mid6) at (-1,-.5) ;
\diagram{
(a4) --[ultra thick,](mid6),
(a3) --[ultra thick,](mid3),
(a2) --[ultra thick,](mid4),
(a1) --[ultra thick,](mid5),
(mid1) --[ultra thick,](mid2),
(mid6) --[ultra thick,](mid2),
(mid1) --[ultra thick,](mid6),
(mid1) --[ultra thick,](mid4),
(mid5) --[ultra thick,](mid3),
(mid5) --[ultra thick,red](mid2),
(mid3) --[ultra thick,](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

%%% Jacobi 1 end %%%

%%% Jacobi 2 start %%%

\newcommand{\JacobiTwoCrossedBoxOne}{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1.5,1){2};
\vertex (a2) at (1.5,-1){4};
\vertex (a3) at (1.5,1){3};
\vertex (a4) at (-1.5,-1){1};
\vertex (mid1) at (0,-.5);
\vertex (mid2) at (0,.5);
\vertex (mid3) at (1,.5);
\vertex (mid4) at (1,-.5);
\vertex (mid5) at (-1,.5);
\vertex (mid6) at (-1,-.5);
\vertex (mid7) at (-.5,0) {};
\diagram{
(a4) --[ultra thick,](mid6),
(a3) --[ultra thick,](mid3),
(a2) --[ultra thick,](mid4),
(a1) --[ultra thick,](mid5),
(mid1) --[ultra thick,](mid6),
(mid3) --[ultra thick,](mid2),
(mid1) --[ultra thick,red](mid4),
(mid5) --[ultra thick,](mid7),
(mid7) --[ultra thick,](mid1),
(mid2) --[ultra thick,](mid6),
(mid5) --[ultra thick,](mid2),
(mid3) --[ultra thick,](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

\newcommand{\JacobiTwoCrossedBoxTwo}{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1.5,1){3};
\vertex (a2) at (1.5,-1){4};
\vertex (a3) at (1.5,1){1};
\vertex (a4) at (-1.5,-1){2};
\vertex (mid1) at (0,-.5);
\vertex (mid2) at (0,.5);
\vertex (mid3) at (1,.5);
\vertex (mid4) at (1,-.5);
\vertex (mid5) at (-1,.5);
\vertex (mid6) at (-1,-.5);
\vertex (mid7) at (-.5,0) {};
\diagram{
(a4) --[ultra thick,](mid6),
(a3) --[ultra thick,](mid3),
(a2) --[ultra thick,](mid4),
(a1) --[ultra thick,](mid5),
(mid1) --[ultra thick,](mid6),
(mid3) --[ultra thick,](mid2),
(mid1) --[ultra thick,red](mid4),
(mid5) --[ultra thick,](mid7),
(mid7) --[ultra thick,](mid1),
(mid2) --[ultra thick,](mid6),
(mid5) --[ultra thick,](mid2),
(mid3) --[ultra thick,](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

\newcommand{\JacobiTwoCrossedBoxThree}{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1.5,1){1};
\vertex (a2) at (1.5,-1){4};
\vertex (a3) at (1.5,1){2};
\vertex (a4) at (-1.5,-1){3};
\vertex (mid1) at (0,-.5);
\vertex (mid2) at (0,.5);
\vertex (mid3) at (1,.5);
\vertex (mid4) at (1,-.5);
\vertex (mid5) at (-1,.5);
\vertex (mid6) at (-1,-.5);
\vertex (mid7) at (-.5,0) {};
\diagram{
(a4) --[ultra thick,](mid6),
(a3) --[ultra thick,](mid3),
(a2) --[ultra thick,](mid4),
(a1) --[ultra thick,](mid5),
(mid1) --[ultra thick,](mid6),
(mid3) --[ultra thick,](mid2),
(mid1) --[ultra thick,red](mid4),
(mid5) --[ultra thick,](mid7),
(mid7) --[ultra thick,](mid1),
(mid2) --[ultra thick,](mid6),
(mid5) --[ultra thick,](mid2),
(mid3) --[ultra thick,](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

%%% Jacobi 2 end %%%

\newcommand{\simplebox}{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1,1){2};
\vertex (a2) at (1,-1){4};
\vertex (a3) at (1,1){3};
\vertex (a4) at (-1,-1){1};
\vertex (mid3) at (.35,.35);
\vertex (mid4) at (.35,-.35);
\vertex (mid5) at (-.35,.35);
\vertex (mid6) at (-.35,-.35);
\diagram{(mid4) --[ultra thick,nhpRed,quarter right](mid3),
(mid5) --[ultra thick,nhpRed,quarter right](mid6),
(mid3) --[ultra thick,nhpRed,quarter right](mid5),
(mid6) --[ultra thick,nhpRed,quarter right](mid4),
(mid6) --[ultra thick,fermion2](a4),
(mid3) --[ultra thick,fermion2](a3),
(mid4) --[ultra thick,fermion2](a2),
(mid5) --[ultra thick,fermion2](a1),
};
\end{feynman}
\end{tikzpicture}
}
}

@@

@@

\newcommand{\dBox}[7]{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1.5,1){2};
\vertex (a2) at (1.5,-1){4};
\vertex (a3) at (1.5,1){3};
\vertex (a4) at (-1.5,-1){1};
\vertex (mid1) at (0,-.5);
\vertex (mid2) at (0,.5);
\vertex (mid3) at (1,.5) ;
\vertex (mid4) at (1,-.5) ;
\vertex (mid5) at (-1,.5);
\vertex (mid6) at (-1,-.5) ;
\diagram{
(a4) --[ultra thick](mid6),
(a3) --[ultra thick,](mid3),
(a2) --[ultra thick,](mid4),
(a1) --[ultra thick,](mid5),
(mid1) --[ultra thick,#1](mid2),
(mid3) --[ultra thick,#2](mid2),
(mid1) --[ultra thick,#3](mid6),
(mid1) --[ultra thick,#4](mid4),
(mid5) --[ultra thick,#5](mid2),
(mid5) --[ultra thick,#6](mid6),
(mid3) --[ultra thick,#7](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

@@

\def\tree{{\rm tree}}
\def\pol{\varepsilon}
\def\Tr{\, {\rm Tr}}
\def\tr{\, {\rm tr}}
\def\eps{\varepsilon}
\def\e{\varepsilon}
\def\ep{\varepsilon}
\def\SYM{MSYM}
\def\nn{\nonumber}
\def\sec#1{section~\ref{#1}}
\def\eqn#1{eq.~(\ref{#1})}
\def\Eqn#1{Equation~(\ref{#1})}
\def\eqns#1#2{eqs.~(\ref{#1}) and~(\ref{#2})}
\def\Eqns#1#2{Eqs.~(\ref{#1}) and~(\ref{#2})}
\def\Figref#1{Fig.~\ref{#1}}
\def\secref#1{section~\ref{#1}}
\def\Neqfour{{{\cal N}=4}}
\def\NeqFour{{{\cal N}=4}}
\def\Neqeight{{{\cal N}=8}}
\def\NeqEight{{{\cal N}=8}}
\def\NeqOne{{{\cal N}=1}}
\def\Fact{{\cal F}}
\def\f{\widetilde f}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}
\def\Ksl{{\s K}}
\def\ksl{\s{k}}
\def\Perm{{\cal P}}
\def\M{{\cal M}}
\def\ve{\varepsilon}
\def\tlambda{{\tilde\lambda}}
\def\MHVbar{$\overline{\hbox{MHV}}$}
\def\NMHVbar{$\overline{\hbox{NMHV}}$}
\def\P{{\rm P}}
\def\NHP{{\rm NHP}}
\def\mud{\lambda}
\def\bowtie{{\rm bow\mbox{-}tie}}
\newcommand{\cred}{\bf \color{red}}
 \newcommand{\cblue}{\color{blue}}
 \definecolor{MattOrange}{rgb}{1.0,0.4,0.2}
\newcommand{\cob}{ \bf \color{MattOrange}}
\newcommand{\andd}{\ , \quad \text{and}  \quad}
\newcommand{\forr}{\ , \quad \text{for}  \quad}

@@

\def\dj#1{{\color{NUpurple}\it \bf JJ: #1}}

\newcommand{\draftnoteJM}[1]{\textbf{\color{blue}[#1]}}

\author[1]{Alex Edison,}
\author[1]{James Mangan,}
\author[1]{Nicolas H. Pavao}

\affiliation[1]{Department of Physics and Astronomy, Northwestern
  University, Evanston, Illinois 60208, USA}

\title{Towards Globally Color-Dual All-Loop Integrands}

@@

  \newpage

@@

\section{Introduction}

\label{sec:intro} Some refs. \cite{BCJreview, Bern:2022wqg, Adamo:2022dcm,Bern:2012uf, Neq44np, GravityFour,Bjerrum-Bohr:2013iza,Edison:2020uzf,Edison:2022jln,Cheung2016prv,He:2017spx,OneTwoLoopPureYMBCJ, Mogull:2015adi, Bern:2015ooa, Geyer:2019hnn,Johansson:2017bfl,Chen:2019ywi,Chen:2021chy,Brandhuber:2021bsf,Cheung:2021zvb,Ben-Shahar:2021zww,Cheung:2022mix, Ben-Shahar:2022ixa,Cachazo:2014xea,Carrasco:2016ldy,Elvang:2020kuj,Bern:2007xj,Carrasco:2013ypa,Craig:2019zkf,Monteiro:2022nqt,Bern:2017tuc,Bern:2017rjw,Bern:2019isl,Goroff:1985sz,Bern:2013uka,Alishahiha:2004eh,Creminelli:2005hu,Fergusson:2008ra,Carrasco:2015pla,Carrasco:2015rva,Carrasco:2015uma,BICEP:2021xfz,Kallosh:2021mnu,Green:1982sw,Mafra:2016mcc,Broedel:2013tta,Carrasco:2016ygv,Azevedo:2018dgo,Anastasiou:2004vj,vonManteuffel:2012np,Smirnov:2014hma,vonManteuffel:2014ixa,Smirnov:2019qkx,Smirnov:2020quc,Usovitsch:2020jrk,Maierhofer:2018gpa,Carrasco:2019yyn,Carrasco:2021ptp,Chi:2021mio,Bonnefoy:2021qgu,Carrasco:2022lbm,Carrasco:2022sck,Pavao:2022kog,Chen:2022shl,Chen:2023dcx,Brown:2023srz,Carrasco:2022jxn,Caron-Huot:2016icg, Chiodaroli:2021eug,Cangemi:2022abk,Cangemi:2022bew,Geiser:2022exp,Cheung:2022mkw,Fonseca:2019yya,Hays:2018zze,Alioli:2022fng}

\section{Review}
The goal is this paper is to compute $D$-dimensional color-dual numerators beyond one-loop. To this end compute two-loop color-dual numerators for NLSM that globally satisfy the duality between color and kinematics and elucidate the color-dual structure expected of Yang-Mills at all-loop order. To set the stage, it is worth distinguishing between the algebraic properties of functionally symmetric kinematics that satisfy color-kinematics globally, and some of the other constructions that appear in the literature.

@@

\subsection{Self-dual Yang-Mills}

@@

where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength. Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:

@@

Applying this coordinate transformation to the self-dual condition of \eqn{SDcon}, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the 4D self-dual condition:

@@

A_w = 0\,, \qquad \partial_u A_v = \partial_w A_{\bar{w}}\,.

@@

The second equation implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom, which we call $\Psi$. This constraint is immediately satisfied with the following definition of the gauge field:

@@

@@

Expanding out the equations of motion for the Yang-Mills Lagrangian, yields the following expression in terms of the gauge fields:
D^\mu F^{\mu\nu} =0\qquad  \Rightarrow\qquad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0

@@

@@

\subsection{ZM-theory} The Lagrangian for Zakharov-Mikhailov (ZM) theory is a simple $SU(N)$ scalar theory defined in two spacetime dimensions:

@@

\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a (\partial^\mu \varphi^b)( \tilde{\partial}_\mu \varphi^c) 

@@

where $\tilde{\partial}_\mu = \epsilon_{\mu\nu}\partial^\nu $ and $\epsilon_{\mu\nu}$ is the two-dimensional Levi-Civita symbol. Expanded out into spacetime components, the momentum space Feynman rule for this theory is simply:

>>>>

\documentclass[11pt,letter]{article}
\pdfoutput=1
\usepackage{jheppub}
\usepackage{amsmath,amssymb}
\usepackage[dvipsnames]{xcolor}
%\usepackage{hyperref}
\usepackage{xspace}
\usepackage{ifdraft}
\usepackage{epstopdf}
\usepackage{slashed}
\usepackage{tocloft}
\renewcommand{\cftdot}{.}
\renewcommand{\cftsubsecleader}{\cftdotfill{\cftdotsep}}
\usepackage{diagbox}
\usepackage{colortbl}
\usepackage{bbold}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{stackengine}
\def\RA{\rlap{\scalebox{1.6}{$\leftrightarrow$}}}
\def\DA{\smash{\bclap{\scalebox{1.6}{$\downarrow$}}}}
\def\mystrut{\rule[-2ex]{0ex}{6ex}}

@@

\usepackage[framemethod=default]{mdframed}
\newmdenv[skipabove=7pt,
skipbelow=7pt,
rightline=false,
leftline=false,
topline=false,
bottomline=false,
backgroundcolor=gray!15,
linecolor=gray,
innerleftmargin=5pt,
innerrightmargin=5pt,
innertopmargin=5pt,
innerbottommargin=5pt,
leftmargin=0cm,
rightmargin=0cm,
linewidth=4pt]{eBox}

\tikzset{graviton/.style={decorate, decoration={snake, amplitude=.4mm, segment length=1.5mm, pre length=.5mm, post length=.5mm}, double}}
\tikzfeynmanset{compat=1.1.0}
\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
\usetikzlibrary{external}  
          %% Load the `external` library
\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
\tikzexternalize[                     %% Activate externalization
  prefix=images/,                    %% Avoid cluttering the directory
 system call={                       %% Use lualatex in system call
    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
  },
]
\tikzfeynmanset{
  fermion2/.style={
    /tikz/postaction={
      /tikz/decoration={
        markings,
        mark=at position 0.8 with {
          \arrow{>[length=6pt, width=7pt]};
        },
      },
      /tikz/decorate=true,
    },
  },
}

@@

\newcommand{\simplebox}{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1,1){2};
\vertex (a2) at (1,-1){4};
\vertex (a3) at (1,1){3};
\vertex (a4) at (-1,-1){1};
\vertex (mid3) at (.35,.35);
\vertex (mid4) at (.35,-.35);
\vertex (mid5) at (-.35,.35);
\vertex (mid6) at (-.35,-.35);
\diagram{(mid4) --[ultra thick,nhpRed](mid3),
(mid5) --[ultra thick,nhpRed](mid6),
(mid3) --[ultra thick,nhpRed](mid5),
(mid6) --[ultra thick,nhpRed](mid4),
(mid6) --[ultra thick,fermion2](a4),
(mid3) --[ultra thick,fermion2](a3),
(mid4) --[ultra thick,fermion2](a2),
(mid5) --[ultra thick,fermion2](a1),
};
\vertex [dot, scale=1.6](mid3a) at (.35,.35){};
\vertex [dot, scale=1.1,hgrey0](mid3b) at (.35,.35){};
\vertex [dot, scale=1.6](mid4a) at (-.35,.35){};
\vertex [dot, scale=1.1,hgrey0](mid4b) at (-.35,.35){};
\vertex [dot, scale=1.6](mid5a) at (.35,-.35){};
\vertex [dot, scale=1.1,hgrey0](mid5b) at (.35,-.35){};
\vertex [dot, scale=1.6](mid6a) at (-.35,-.35){};
\vertex [dot, scale=1.1,hgrey0](mid6b) at (-.35,-.35){};
\end{feynman}
\end{tikzpicture}
}
}

@@

\newcommand{\AcubicB}[9]{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (0,0){};
\vertex (a2) at (-1.55,.85){2};
\vertex (a3) at (-1.55,-.85){1};
\vertex [dot, scale=2.6](mid1) at (-.85,0){};
\vertex [dot, scale=2.6](mid2) at (-.85,0){};
\vertex [dot, scale=2,#1](mid3) at (-.85,0){};
\vertex (a4) at (1.55,.85){3};
\vertex (a5) at (1.55,-.85){4};
\vertex [dot, scale=2.6](mid4) at (.85,0){};
\vertex [dot, scale=2.6](mid5) at (.85,0){};
\vertex [dot, scale=2,#1](mid6) at (.85,0){};
\diagram{
(mid1) --[ultra thick,#2,#3](a3),
(mid1) --[ultra thick,#4,#5](a2),
(mid4) --[ultra thick,#8,#9](a4),
(mid4) --[ultra thick,#8,#9](a5),
(mid1) --[ultra thick,#6,#7](a1),
(a1) --[ultra thick,#6,#7](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

@@

\newcommand{\dBox}[7]{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1.5,1){2};
\vertex (a2) at (1.5,-1){4};
\vertex (a3) at (1.5,1){3};
\vertex (a4) at (-1.5,-1){1};
\vertex (mid1) at (0,-.5);
\vertex (mid2) at (0,.5);
\vertex (mid3) at (1,.5) ;
\vertex (mid4) at (1,-.5) ;
\vertex (mid5) at (-1,.5);
\vertex (mid6) at (-1,-.5) ;
\diagram{
(a4) --[ultra thick,](mid6),
(a3) --[ultra thick,](mid3),
(a2) --[ultra thick,](mid4),
(a1) --[ultra thick,](mid5),
(mid1) --[ultra thick,#1](mid2),
(mid3) --[ultra thick,#2](mid2),
(mid1) --[ultra thick,#3](mid6),
(mid1) --[ultra thick,#4](mid4),
(mid5) --[ultra thick,#5](mid2),
(mid5) --[ultra thick,#6](mid6),
(mid3) --[ultra thick,#7](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

@@

\def\tree{{\rm tree}}
\def\pol{\varepsilon}
\def\Tr{\, {\rm Tr}}
\def\tr{\, {\rm tr}}
\def\eps{\varepsilon}
\def\e{\varepsilon}
\def\ep{\varepsilon}
\def\SYM{MSYM}
\def\nn{\nonumber}
\def\sec#1{section~\ref{#1}}
\def\eqn#1{(\ref{#1})}
\def\Eqn#1{Equation~(\ref{#1})}
\def\eqns#1#2{eqs.~(\ref{#1}) and~(\ref{#2})}
\def\Eqns#1#2{Eqs.~(\ref{#1}) and~(\ref{#2})}
\def\Figref#1{Fig.~\ref{#1}}
\def\secref#1{section~\ref{#1}}
\def\Neqfour{{{\cal N}=4}}
\def\NeqFour{{{\cal N}=4}}
\def\Neqeight{{{\cal N}=8}}
\def\NeqEight{{{\cal N}=8}}
\def\NeqOne{{{\cal N}=1}}
\def\Fact{{\cal F}}
\def\f{\widetilde f}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}
\def\Ksl{{\s K}}
\def\ksl{\s{k}}
\def\Perm{{\cal P}}
\def\M{{\cal M}}
\def\ve{\varepsilon}
\def\tlambda{{\tilde\lambda}}
\def\MHVbar{$\overline{\hbox{MHV}}$}
\def\NMHVbar{$\overline{\hbox{NMHV}}$}
\def\P{{\rm P}}
\def\NHP{{\rm NHP}}
\def\mud{\lambda}
\def\bowtie{{\rm bow\mbox{-}tie}}
\newcommand{\cred}{\bf \color{red}}
 \newcommand{\cblue}{\color{blue}}
 \definecolor{MattOrange}{rgb}{1.0,0.4,0.2}
\newcommand{\cob}{ \bf \color{MattOrange}}
\newcommand{\andd}{\ , \quad \text{and}  \quad}
\newcommand{\forr}{\ , \quad \text{for}  \quad}

@@

\author{Alex Edison,}
\author{James Mangan,}
\author{and Nicolas H. Pavao}

\affiliation{Department of Physics and Astronomy, Northwestern
  University, Evanston, Illinois 60208, USA}

\emailAdd{alexander.edison@northwestern.edu, james.mangan@northwestern.edu, pavao@u.northwestern.edu}

\title{\center Towards Globally Color-Dual All-Loop Integrands}

@@

\makeatletter
\gdef\@fpheader{\,}

@@

\section{Introduction}
\section{Review}
 To set the stage, it is worth distinguishing between the algebraic properties of functionally symmetric kinematics that satisfy color-kinematics globally, and some of the other constructions that appear in the literature.

@@

\subsection{Color-dual Amplitudes}
Review of BCJ relations and Jacobi relations off-shell. Justify kinematic algebra in an off-shell framework by talking about on-shell construction. yada yada yada
\subsection{Color-dual Lagrangians} In the next section we will construct one-loop color-dual numerators using Lagrangian descriptions that are manifestly color-dual. As we will show, taking forward limits of tree-level numerators works as long as one can construct an off-shell description with a Lagrangian. Here we briefly review the off-shell examples of the kinematic algebra that will be relevant in this paper.  
\paragraph{Self-Dual Yang-Mills} The first example in the literature \cite{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):

@@

where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength. Solutions to the self-dual condition automatically satisfy the Yang-Mills equation of motion due to the Bianchi identity:
D^\mu F^{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
Solutions to \eqn{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills. In this paper, we will focus on the perturbative aspects of this constraint. Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:

@@

Applying this coordinate transformation to the self-dual condition of \eqn{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
\begin{align} \label{SDLightCone1}
F_{uw} &=0\,,
\\
 \label{SDLightCone2}
 F_{uv} &= F_{w\bar{w}}\,,
\\
 \label{SDLightCone3}
 F_{v\bar{w}} &= 0\,,
\end{align}
Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:

@@

A_u=0 \text{ and } \eqn{SDLightCone1} \quad\Rightarrow \quad A_w=0

@@

The second equation \eqn{SDLightCone2}  then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom

@@

A_w=0\,,\,A_u=0 \text{ and }\eqn{SDLightCone2} \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
\be\label{SDDef}

@@

Using this definition on the final self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
\be\label{SDEOM}
\eqn{SDLightCone1} \text{ and } \eqn{SDDef} \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0

@@

\begin{eBox}

@@

\end{eBox}
The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:

@@

\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}

@@

In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}. In this form, we can see the effect \eqn{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex. Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.

As we will show in \sect{}, the color-dual nature of SDYM can be understood as a direct consequence of isolating the \textit{cubic-sector} of the full Yang-Mills amplitudes by projecting along particular on-shell states. For this reason, the color-dual nature depends critically on the loop order of the amplitude and does not hold generically beyond one-loop.

Next we will briefly describe a 2D scalar theory, Zakharov-Mikhailov (ZM) theory, whose equations of motion bear a striking resemblance to the SDYM equatioi of motion given above in \eqn{SDEOM}.
\paragraph{ZM-theory} The Lagrangian for Zakharov-Mikhailov (ZM) theory is a simple $SU(N)$ scalar theory defined in two spacetime dimensions:
\begin{eBox}
\be
\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a (\partial^\mu \varphi^b)( \tilde{\partial}_\mu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right]
\ee
\end{eBox}
where $\tilde{\partial}_\mu = \epsilon_{\mu\nu}\partial^\nu $ and $\epsilon_{\mu\nu}$ is the two-dimensional Levi-Civita symbol. Expanded out into spacetime components, the momentum space Feynman rule for this theory is simply:
\be
\langle ab\rangle \equiv p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle 
\ee
 From the interaction part of the Lagrangian, we can see that the three-point vertex is (1) functionally symmetric and (2) the kinematics are completely anti-symmetric: 
\be
\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
\ee
This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality. In addition to anti-symmetry, the cubic graphs will satisfy jacobi off-shell on any internal edge due to the delta function identity of 2D Levi-Civita symbols:
\be
\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle = \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c=0
\ee
Theories with this property are the creme de la creme of color-dual gauge theories as they trivially satisfy color-kinematic algebraic relations off-shell. This allows one to trivially promote the duality from tree-level to all-loop order by dressing each cubic vertex with its own kinematic structure constant.

While the color-dual nature of ZM theory is rather elegant, the loop-level construction introduces complications when applying dimensional regularization. Similar to the difficulties of renormalizing chiral fermions \cite{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions. As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg. 
\paragraph{YZ-Theory} Thus far, the two color-dual Lagrangians we have discussed make explicit reference to the spacetime dimension ($D=4$ for SDYM, and $D=2$ for ZM theory). This makes them poorly suited for constructing dimensionally regulated integrals in loop-level amplitudes. Here we briefly review YZ-theory, which is a honest $D$-dimensional theory first proposed by Cheung and Hsien \cite{Cheung2016prv} for the purpose of describing nonlinear sigma model (NLSM) scattering. One can understand YZ-theory as a particular dimensional reduction of Yang-Mills in $D=2d+1$ dimensions, down to $d$ dimensions.
